Hierarchical Dispatching and Overriding

### 2017-09-06 NewVersion/sections/Auxiliary.tex
new
filename uppercase
more fixing

    \inferrule* [left=]
    { set1 = \; \{ K <: J \; $and$ \; K >: I \; | \; m \in \overrideSet(K, K) \} \\
        set2 = \; \{ K >: J \; | \; m \in \overrideSet(K, K) \} }
    {\mostSpecific(m, I, J) = \left\{{\begin{tabular}{ll}
                $prune(set1)$ & if $set1$ is not empty \\ $prune(set2)$ & otherwise
            \end{tabular}}\right.}

    \inferrule* [left=]
        { set = \; \{ K <: J \; $and$ \; K >: I \; | \;
            m \in \overrideSet(K, J)  \} }
        {\mostSpecificOverride(m, I, J) = prune(set)}

    prune(set) = \{I \in set \; | \; \nexists J \in set, J <: I, J \neq I \}

    \inferrule* [left=]
    {   \interface{I}{I}{M}
        \\ J \in \overline{I} }
    {\ext(I, J)}

@@

\begin{figure*}[t]
    \centering
    \vspace{-1ex}
    \begin{tabular}{ccc}
        \includegraphics[width=1.5cm]{pics/p1.pdf}\hspace{4pt} &
        \includegraphics[width=1.5cm]{pics/p2.pdf}\hspace{4pt} &
        \includegraphics[width=1.5cm]{pics/p3.pdf}\hspace{4pt} \\
        (a) $\mbody(m,C,A) = (A,...)$\ \ \  & (b) $\mbody(m,C,A) = (C,...)$\ \ \  & (c) $\mbody(m,C,A) = (C,...)$
    \end{tabular} \\
   \begin{tabular}{cc}
    \includegraphics[height=3cm]{pics/p4.pdf}\hspace{4pt} &
    \includegraphics[height=3cm]{pics/p5.pdf}\hspace{4pt} \\ 
    (d) $\mbody(m,D,A) = \keyword{undefined}$\ \ \  & (e) $\mbody(m,D,A) = \keyword{undefined}$
   \end{tabular}
    \caption{Examples on $\mbody$. ``$\uparrow$'' stands for hierarchical overriding.}\label{fig:examplesmbody}
    %\saveSpaceFig
\end{figure*}

@@

\subsection{$\mbodyStatic$}
The auxilary function $\mbodyStatic$ serves for method loopup for static method invocation. 
The brief description of the algorithm follows:
\begin{mathpar}
    \inferrule* [left=]
        {  \mostSpecific(m, I, I) = \{J\} \\
            \kwinterface \; J \; \kwextends \; \overline{J} \; \{\method{I_e}{m}{I_x}{x}{J}{e_0}\ldots\}}
        {\mbodyStatic(m, I) = (J, \overline{I_x} \; \overline{x}, I_e \; e_0)}

    \inferrule* [left=]
        {  \mostSpecific(m, I, I) = \{J\} \\
            \kwinterface \; J \; \kwextends \; \overline{J} \; \{\absmethod{I_e}{m}{I_x}{x}{J}\ldots\}}
        {\mbodyStatic(m, I) = (J, \overline{I_x} \; \overline{x}, I_e \; \o)}
\end{mathpar}

>>>>

    \inferrule* [left=]
    { set1 = \; \{K\mid I <: K, \; K <: J\; $and$\; m \in \overrideSet(K, K) \} \\
        set2 = \; \{K\mid  J <: K \; $and$\; m \in \overrideSet(K, K) \} }
    {\mostSpecific(m, I, J) = \left\{{\begin{tabular}{ll}
                $prune(set1)$ & if $set1$ is not empty \\ $prune(set2)$ & otherwise
            \end{tabular}}\right.}

    \inferrule* [left=]
        { set = \; \{ K\mid I <: K, \; K <: J\; $and$ \;
            m \in \overrideSet(K, J)  \} }
        {\mostSpecificOverride(m, I, J) = prune(set)}

    prune(set) = \{I \in set \; | \; \nexists J \in set\setminus I, J <: I\}

    \inferrule* [left=]
    {   \interface{I}{I}{M}
        \\ J \in \overline{I} }
    {\ext(I, J) \marco{Is this ever used?}}

@@

\begin{figure*}[t]
    \centering
    \vspace{-1ex}
    \begin{tabular}{ccc}
        \includegraphics[width=1.5cm]{pics/P1.pdf}\hspace{4pt} &
        \includegraphics[width=1.5cm]{pics/P2.pdf}\hspace{4pt} &
        \includegraphics[width=1.5cm]{pics/P3.pdf}\hspace{4pt} \\
        (a) $\mbody(m,C,A) = (A,...)$\ \ \  & (b) $\mbody(m,C,A) = (C,...)$\ \ \  & (c) $\mbody(m,C,A) = (C,...)$
    \end{tabular} \\
   \begin{tabular}{cc}
    \includegraphics[height=3cm]{pics/P4.pdf}\hspace{4pt} &
    \includegraphics[height=3cm]{pics/P5.pdf}\hspace{4pt} \\ 
    (d) $\mbody(m,D,A) = \keyword{undefined}$\ \ \  & (e) $\mbody(m,D,A) = \keyword{undefined}$
   \end{tabular}
    \caption{Examples on $\mbody$. ``$\uparrow$'' stands for hierarchical overriding.}\label{fig:examplesmbody}
    %\saveSpaceFig
\end{figure*}

@@

\subsection{$\mbodyStatic$}
The auxilary function $\mbodyStatic$ serves for method loopup for static method invocation. 
The brief description of the algorithm follows:
\begin{mathpar}
    \inferrule* [left=]
        {  %\mostSpecific(m, I, I) = \{J\} \\
            \kwinterface \; J \; \kwextends \; \overline{J} \; \{\method{I_e}{m}{I_x}{x}{J}{e_0}\ldots\}}
        {\mbodyStatic(m, J, J') = (J, \overline{I_x} \; \overline{x}, I_e \; e_0)}

    \inferrule* [left=]
        {  %\mostSpecific(m, I, I) = \{J\} \\
            \kwinterface \; J \; \kwextends \; \overline{J} \; \{\absmethod{I_e}{m}{I_x}{x}{J}\ldots\}}
        {\mbodyStatic(m, J, J') = (J, \overline{I_x} \; \overline{x}, I_e \; \o)}
\end{mathpar}
